\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-05 ZpL/ZpL.tex

In this paper, we describe an implementation of this idea in \sage \cite{sage}.
Rather than attaching a precision to each element, we store the precision of
many elements together by tracking a precision module for the whole collection
of variables.  As variables are created and destroyed, we update a matrix whose
rows represent the vectors in the module.  Information about the precision
of elements is extracted from the matrix as necessary.
Concretely, our package provides two new \sage 
parents\footnote{Parents in \sage are the analogues of container objects 
in computer science. Basically it corresponds to the implementation of a 
concrete mathematical structure, as the ring of $p$-adic integers.}, 
namely \ZpLC and \ZpLF (and their fraction fields \QpLC and \QpLF). The 
acronyms \LC and \LF stand for ``lattice-cap'' and ``lattice-float''
respectively (see \S \ref{sec:implementation} for details). Our package 
is merged in the standard distribution of \sage since version 8.2.

>>>>

In this paper, we describe an implementation of this idea in \sage \cite{sage}.
Rather than attaching a precision to each element, we store the precision of
many elements together by tracking a precision module\footnote{Throughout
the paper, the word ``module'' has its mathematical meaning: it denotes 
an additive group endowed with an external product by scalars in $\Zp$.} 
for the whole collection of variables.  As variables are created and 
destroyed, we update a matrix whose rows represent the vectors in the 
module.  Information about the precision of elements is extracted from 
the matrix as necessary.
Concretely, our package provides two new \sage 
parents\footnote{Parents in \sage are the analogues of container objects 
in computer science. Basically it corresponds to the implementation of a 
concrete mathematical structure, as the ring of $p$-adic integers.}, 
namely \ZpLC and \ZpLF (and their fraction fields \QpLC and \QpLF). The 
acronyms \LC and \LF stand for ``lattice-cap'' and ``lattice-float''
respectively (see \S \ref{sec:implementation} for details). Our package 
is merged in the standard distribution of \sage since version 8.2.
